---
title: "A study about salary difference in Brazil"
author: "Marcely Zanon Boito"
date: "December 21, 2016"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Data sets
We have six data sets, each one representing a different working field: architecture, medicine, engineering, economy, law and street cleaning. All these datasets have information about people registred as payed professionals for that area, and they have information about number of hours, salary average, the salary minimum per hour, the gender, the age and employment time.

## The Problem and the Hypothesis:
Having information about different six different working fields at Brazil, we want to identify:

1. Where we have the bigger salary gaps per gender;

2. How time of scolarity affects:

  + 2.1. The salary;
  
  + 2.2. The employment time;
  
3. The bigger estability (measured as average employment time);

4. How age affect the salary:

  + 4.1. When a person gets older in Brazil, do they gain more or less money?

## First Dataset: Economist set
We have seven variables in this dataset: contract hours, age, gender, scholarity, average salary, minimum per hour, and employment time.



```{r }
load(file="data/economist.Rdata")
summary(economist)
```

* Scholarity:

```{r}
library(ggplot2)
meanE <- mean(economist$Scholarity)
std <- sd(economist$Scholarity)
ggplot(data = economist, aes(economist$Scholarity) ) + geom_bar(fill="white", colour = "black") + labs(x= "scholarity")+ geom_vline(aes(xintercept = meanE, colour = "mean")) + geom_vline(aes(xintercept = (meanE + std), colour = "std"), linetype = "dashed") +  geom_vline(aes(xintercept = (meanE - std), colour = "std"), linetype = "dashed")  + scale_colour_manual(name = "Central Tendency Measurements", breaks = c("mean", "std"), values= c(mean = "red", std = "blue")) 
```

Looking at the difference of frequency between the different scholarity levels in the dataset, I believe is going to be difficult to infer things based on the level of scholarity, since most of the dataset falls in the category 9.

* Age:

```{r}
meanE <- mean(economist$age)
std <- sd(economist$age)
ggplot(data = economist, aes(economist$age)) + geom_bar(fill="white", colour = "black") + labs(x= "age")+ geom_vline(aes(xintercept = meanE, colour = "mean")) + geom_vline(aes(xintercept = (meanE + std), colour = "std"), linetype = "dashed") +  geom_vline(aes(xintercept = (meanE - std), colour = "std"), linetype = "dashed")  + geom_vline(aes(xintercept = median(economist$age), colour = "median"))   + 
  scale_colour_manual(name = "Central Tendency Measurements", breaks = c("mean", "std","median"), values= c(mean = "red", std = "blue", median = "orange")) 


```


